\documentclass[12pt,a4paper]{scrartcl}
\usepackage{rawfonts}
\usepackage{amssymb}

\usepackage{color}
\definecolor{astral}{RGB}{46,116,181}
\definecolor{myblue}{rgb}{0.25,0.25,0.5}

\usepackage{sectsty}
\sectionfont{\color{astral}}

\usepackage[colorlinks=true, urlcolor=blue, linkcolor=red]{hyperref}

\setlength{\parskip}{1.5ex plus 0.5ex minus 0.5ex}

\begin{document}
\title{\color{myblue}{Comparing K-Means and Other Algorithms for Data Clustering\break in Assembly. }}

\author{Héctor S. Enrique}
\date{ january 30, 2024}
\maketitle

\section{Purpose:}

	See presentation and discussion in \href{https://masm32.com/board/index.php?topic=11649.0}{ Masm32 Forum} 

\section{Running the Program: }

    \begin{itemize}
        \item Step 1: Select from Menu Data one data set. If you want to use default set or already loaded set, then skip this step. 
        \item Step 2: Select from Menu File  $\displaystyle >$
 Load Data. If you want to use already loaded set, then skip this step. 
        \item Step 3:  Select from Menu Strategy the algorithm you want. If you want to use default stratey or already select algorithm, then skip this step. 
        \item Step 4 : Only if you seleted K-Means or Hierarchical strategies. Select from  Menu Cluster the number of clusters. In this examples the author use 3-clusters for data1 and data2, and  2-clusters for data 3. 
        \item Step 5 : Select from Menu File $\displaystyle >$ Run 
        \item Step 6 : Go to Step1 to test more things. 
     \end{itemize}

\section{Additional Reading}

	\href{https://www.codeproject.com/Articles/5375470/Comparing-K-Means-and-Others-Algorithms-for-Data-C}{Comparing K-Means and Others Algorithms for Data Clustering} by Nicolás Descartes 

\thispagestyle{empty}

\end{document}